Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2017-06-19 documents/TriangleScenarioArXiv/ts.tex
Pushing ShareLatex to GitHub

    \begin{definition}
        \label{def:inflation}
        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
        \[ \forall n' \in \nodes': \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \eq \label{eq:inflation_defn}\]
    \end{definition}
    \begin{center}
    \begin{figure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral}}
    \caption{The Spiral inflation.}\label{fig:spiral_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
    \caption{The Wagon-Wheel inflation.}\label{fig:wagon_wheel_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure}}
    \caption{The Web Inflation.}\label{fig:the_web_inflation}
    \end{subfigure}
    \caption{Some inflations of the Triangle structure.}
    \label{fig:inflations}
    \end{figure}
    \end{center}
    \begin{center}
    \begin{figure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/triangle_structure_injectable_highlight_1}}
    \caption{$\AnSub[\graph]{A}$}\label{fig:spiral_inflation_iminj1}
    \end{subfigure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_1}}
    \caption{$\AnSub[\graph']{A_1}$}\label{fig:spiral_inflation_inj1}
    \end{subfigure}
    % \par\bigskip % For vertical spacing https://tex.stackexchange.com/questions/120700/vertical-spacing-using-subcaption-package
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/triangle_structure_injectable_highlight_2}}
    \caption{$\AnSub[\graph]{A,C}$}\label{fig:spiral_inflation_iminj2}
    \end{subfigure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_2}}
    \caption{$\AnSub[\graph']{A_2, C_1}$}\label{fig:spiral_inflation_inj2}
    \end{subfigure}
    \caption{Some injectable sets $\Inj[\graph]{\graph'}$ of the Spiral inflation ($\graph'$) and their corresponding images $\ImInj[\graph]{\graph'}$ in the Triangle structure ($\graph$).}
    \label{fig:injectablesets}
    \end{figure}
    \end{center}
    Verbally, for each inflated node $n'$, the ancestral sub-graph of $n'$ in $\graph'$ is homomorphic to its counterpart in $\graph$ where the homomorphism is the removal of the copy-index. For example, the ancestral subgraph of $A$ in the Triangle structure (denoted $\AnSub[\graph]{A}$) is highlighted in \cref{fig:spiral_inflation_iminj1} and is clearly homomorphic to the ancestral subgraph of $A_1$ in the Spiral inflation (denoted $\AnSub[\graph]{A_1}$) depicted in \cref{fig:spiral_inflation_inj1}. Since this ancestral homomorphism exists for each node $n'$ of the Spiral inflation (\cref{fig:spiral_inflation}), it qualifies as a valid inflation of the Triangle structure (\cref{fig:triangle_structure}).

@@

    \setlength{\bibsep}{3pt plus 3pt minus 2pt}
    \bibliographystyle{apsrev4-1}
    % \nocite{apsrev41Control}
    \bibliography{references}

>>>>

    \begin{definition}
        \label{def:inflation}
        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
        \[ \forall n' \in \nodes': \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \eq \label{eq:inflation_defn}\]
    \end{definition}
    \begin{center}
    \begin{figure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral}}
    \caption{The Spiral inflation.}\label{fig:spiral_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
    \caption{The Wagon-Wheel inflation.}\label{fig:wagon_wheel_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure}}
    \caption{The Web Inflation.}\label{fig:the_web_inflation}
    \end{subfigure}
    \caption{Some inflations of the Triangle structure.}
    \label{fig:inflations}
    \end{figure}
    \end{center}
    \begin{center}
    \begin{figure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/triangle_structure_injectable_highlight_1}}
    \caption{$\AnSub[\graph]{A}$}\label{fig:spiral_inflation_iminj1}
    \end{subfigure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_1}}
    \caption{$\AnSub[\graph']{A_1}$}\label{fig:spiral_inflation_inj1}
    \end{subfigure}
    % \par\bigskip % For vertical spacing https://tex.stackexchange.com/questions/120700/vertical-spacing-using-subcaption-package
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/triangle_structure_injectable_highlight_2}}
    \caption{$\AnSub[\graph]{A,C}$}\label{fig:spiral_inflation_iminj2}
    \end{subfigure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_2}}
    \caption{$\AnSub[\graph']{A_2, C_1}$}\label{fig:spiral_inflation_inj2}
    \end{subfigure}
    \caption{Some injectable sets $\Inj[\graph]{\graph'}$ of the Spiral inflation ($\graph'$) and their corresponding images $\ImInj[\graph]{\graph'}$ in the Triangle structure ($\graph$).}
    \label{fig:injectablesets}
    \end{figure}
    \end{center}
    For each inflated node $n'$, the ancestral sub-graph of $n'$ in $\graph'$ is homomorphic to its counterpart in $\graph$ where the homomorphism is the removal of the copy-index. For example, the ancestral subgraph of $A$ in the Triangle structure (denoted $\AnSub[\graph]{A}$) is highlighted in \cref{fig:spiral_inflation_iminj1} and is clearly homomorphic to the ancestral subgraph of $A_1$ in the Spiral inflation (denoted $\AnSub[\graph]{A_1}$) depicted in \cref{fig:spiral_inflation_inj1}. Since this ancestral homomorphism exists for each node $n'$ of the Spiral inflation (\cref{fig:spiral_inflation}), it qualifies as a valid inflation of the Triangle structure (\cref{fig:triangle_structure}).

@@

    \setlength{\bibsep}{3pt plus 3pt minus 2pt}
    \bibliographystyle{apsrev4-1}
    \nocite{apsrev41Control}
    \bibliography{references}
